Aa Language Reference Manual

### 2015-10-02 v2/Ahir-asm/devel/docs/AaLRM.tex
Fixed bug in generating volatile vhdl model.

\section{Inline and Macro Modules}

@@

However, in order to give the \Aa programmer
more flexibility,  a module in \Aa may be marked
to be inlined or substituted into the program
at the point of the call.  The AhirV2 utility
{\bf AaOpt} is responsible for this substitution.

@@

$module [add_check] $in (p: $uint<32> q: $uint<32>) 
    $out (r : $uint<32>) $is
{
    $call add (p q) (r)
}
\end{verbatim}
is translated to
\begin{verbatim}
$module [add_check]
$in ( p : $uint<32>   q : $uint<32>  )
$out ( r : $uint<32>  )
$is
{
  $seriesblock[add_18] 
  {
    $parallelblock[InArgs] 
    {
      add_18_a := p
      add_18_b := q
    }
    ( add_18_a => add_18_a add_18_b => add_18_b )
    $seriesblock[body] 
    {
      add_18_c := (add_18_a + add_18_b)
    }
    (  add_18_c => add_18_c )
    $parallelblock[OutArgs] 
    {
      r := add_18_c
    }
    ( r => r )
  }
  ( r => r )
}
\end{verbatim}
The three step substitution of add into add\_check
is clearly seen.

@@

>>>>

\section{Module classes: pipeline, volatile, operator, inline, macro, foreign }

@@

However, in order to give the \Aa programmer
more flexibility,  a module in \Aa may be marked
as belonging to a particular class.  These
are described below.

\subsection{Pipelined Modules}

A module is marked as a pipeline-module if its
hardware implementation is to be converted into 
a pipeline.  This allows efficient use of the module
resources.

\begin{verbatim}
$pipeline $module [foo] $in (...) $out (...) $is
{
...
}
\end{verbatim}

A pipeline module {\bf must} have {\bf at least} one input
and one output argument.  Further, at least one input argument
must actually be sampled inside the module, and one output argument
must actually be updated inside the module.

\subsection{Operator Modules}

A module is marked as an operator-module if it
is to be substituted at every point where it
is called (thus, multiple instances of the module
will be generated).
This allows low latency access to the module
functionality in hardware.

\begin{verbatim}
$operator $module [foo] $in (...) $out (...) $is
{
...
}
\end{verbatim}

An operator module {\bf must} have {\bf at least} one input
and one output argument.  Further, at least one input argument
must actually be sampled inside the module, and one output argument
must actually be updated inside the module.

An operator module may also be marked as pipelined.
\begin{verbatim}
$pipeline $operator $module [foo] $in (..) $out (..)
\end{verbatim}

\subsection{Volatile Modules}

A module is marked as a volatile-module if 
\begin{itemize}
\item Its hardware implementation is to be 
a combinational (memory-less) circuit.
\item It is to be substituted at every point where it
is called (thus, multiple instances of the module
will be generated).
\end{itemize}
This allows low level implementation control
to the programmer.

\begin{verbatim}
$volatile $module [foo] $in (...) $out (...) $is
{
...
}
\end{verbatim}

A volatile module cannot make any memory accesses or 
reads/writes to pipes.  Inside a volatile module, 
a function call must be to volatile modules only.

@@

$module [add_check] $in (p: $uint<32> q: $uint<32>) 
    $out (r : $uint<32>) $is
{
    $call add (p q) (r)
}
\end{verbatim}
is translated to
\begin{verbatim}
$module [add_check]
$in ( p : $uint<32>   q : $uint<32>  )
$out ( r : $uint<32>  )
$is
{
  $seriesblock[add_18] 
  {
    $parallelblock[InArgs] 
    {
      add_18_a := p
      add_18_b := q
    }
    ( add_18_a => add_18_a add_18_b => add_18_b )
    $seriesblock[body] 
    {
      add_18_c := (add_18_a + add_18_b)
    }
    (  add_18_c => add_18_c )
    $parallelblock[OutArgs] 
    {
      r := add_18_c
    }
    ( r => r )
  }
  ( r => r )
}
\end{verbatim}
The three step substitution of add into add\_check
is clearly seen.  
There are no restrictions on the
module that is being inlined.

@@

There are no restrictions on the
module that is being inlined.
